Interpreting Random Forest Predictions for Firearm Identification Using LIME

### 2019-01-25 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
worked on cleaning up code after rfscore has been added

  # Specify the options to use with lime
  hamby224_lime_inputs <- list(bin_continuous = c(rep(TRUE, 20), rep(FALSE, 2)),
                               quantile_bins = c(rep(TRUE, 5), rep(FALSE, 5), 
                                                 rep(TRUE, 10), rep(TRUE, 2)),
                               nbins = c(rep(2:6, 4), rep(4, 2)),
                               use_density = c(rep(TRUE, 20), TRUE, FALSE),
                               bin_method = c(rep("quantile_bins", 5),
                                              rep("equally_spaced", 5),
                                              rep("tree", 10),
                                              rep("quantile_bins", 2)),
                               response = c(rep(NA, 10), rep("samesource", 5), 
                                            rep("rfscore", 5), rep(NA, 2)))

@@

  hamby224_lime_inputs <- hamby224_lime_inputs %>%
    unlist() %>%
    matrix(ncol = length(hamby224_lime_inputs), 
           dimnames = list(NULL, names(hamby224_lime_inputs))) %>%
    as.data.frame() %>%
    mutate(case = 1:length(hamby224_lime_inputs$quantile_bins)) %>%
    select(case, bin_continuous:response)

@@

  # Reorder the variables of feature_desc and feature_bin for plotting purposes and
  # create new variables of situation and bin_situation
  hamby224_test_explain <- hamby224_test_explain %>%
    mutate(feature_desc = reorder(feature_desc, strictly_less),
           feature_desc = reorder(feature_desc, feature_number),
           feature_desc = reorder(feature_desc, as.numeric(feature))) %>%
    mutate(nbins = as.numeric(as.character(nbins)),
           situation = ifelse(bin_continuous == TRUE & bin_method == "quantile_bins", 
                              sprintf("%.0f quantile bins", nbins),
                              ifelse(bin_continuous == TRUE & bin_method == "equally_spaced",
                                     sprintf("%.0f equally spaced bins", nbins),
                                     ifelse(bin_continuous == TRUE & bin_method == "tree" &
                                              response == "samesource",
                                            sprintf("%.0f samesource tree based bins", nbins),
                                            ifelse(bin_continuous == TRUE & bin_method == "tree" &
                                              response == "rfscore",
                                              sprintf("%.0f rfscore tree based bins", nbins),
                                              ifelse(bin_continuous == FALSE & 
                                                       use_density == TRUE, 
                                                     "kernel density", "normal approximation"))))) %>%
             fct_relevel("2 quantile bins", "3 quantile bins", "4 quantile bins",
                         "5 quantile bins", "6 quantile bins", "2 equally spaced bins",
                         "3 equally spaced bins", "4 equally spaced bins",
                         "5 equally spaced bins", "6 equally spaced bins",
                         "2 samesource tree based bins", "3 samesource tree based bins",
                         "4 samesource tree based bins", "5 samesource tree based bins",
                         "6 samesource tree based bins")) %>%
    mutate(bin_situation = ifelse(bin_method == "quantile_bins" & bin_continuous == TRUE,
                                "quantile bins",
                                ifelse(bin_method == "equally_spaced" & bin_continuous == TRUE,
                                       "equally spaced bins", 
                                       ifelse(bin_method == "tree" & bin_continuous == TRUE & 
                                                response == "samesource",
                                              "samesource tree based bins", 
                                              ifelse(bin_method == "tree" & bin_continuous == TRUE & 
                                                response == "rfscore",
                                                "rfscore tree based bins", "other"))))) %>%
    mutate(bin_situation = factor(bin_situation)) %>%
    select(situation, bin_situation, bin_continuous:response, case:feature_desc,
           feature_bin:strictly_less, data, prediction)

>>>>

  # Specify the input options to use with lime
  hamby224_lime_inputs <- list(bin_continuous = c(rep(TRUE, 20), 
                                                  rep(FALSE, 2)),
                               quantile_bins = c(rep(TRUE, 5), 
                                                 rep(FALSE, 5), 
                                                 rep(TRUE, 12)),
                               nbins = c(rep(2:6, 4), 
                                         rep(4, 2)),
                               use_density = c(rep(TRUE, 20), TRUE, FALSE),
                               bin_method = c(rep("quantile_bins", 5),
                                              rep("equally_spaced", 5),
                                              rep("tree", 10),
                                              rep("quantile_bins", 2)),
                               response = c(rep(NA, 10), 
                                            rep("samesource", 5), 
                                            rep("rfscore", 5), 
                                            rep(NA, 2)))

@@

  # Turn the lime input options into a dataframe before saving it
  hamby224_lime_inputs <- hamby224_lime_inputs %>%
    unlist() %>%
    matrix(ncol = length(hamby224_lime_inputs), 
           dimnames = list(NULL, names(hamby224_lime_inputs))) %>%
    as.data.frame() %>%
    mutate(case = 1:length(hamby224_lime_inputs$quantile_bins)) %>%
    select(case, bin_continuous:response)

@@

  # Reorder the variables of feature_desc and feature_bin for plotting purposes and
  # create new variables of situation and bin_situation
  hamby224_test_explain <- hamby224_test_explain %>%
    mutate(feature_desc = reorder(feature_desc, strictly_less),
           feature_desc = reorder(feature_desc, feature_number),
           feature_desc = reorder(feature_desc, as.numeric(feature))) %>%
    mutate(nbins = as.numeric(as.character(nbins)),
           situation = ifelse(bin_continuous == TRUE & bin_method == "quantile_bins", 
                              sprintf("%.0f quantile", nbins),
                              ifelse(bin_continuous == TRUE & bin_method == "equally_spaced",
                                     sprintf("%.0f equally spaced", nbins),
                                     ifelse(bin_continuous == TRUE & bin_method == "tree" &
                                              response == "samesource",
                                            sprintf("%.0f samesource tree", nbins),
                                            ifelse(bin_continuous == TRUE & bin_method == "tree" &
                                              response == "rfscore",
                                              sprintf("%.0f rfscore tree", nbins),
                                              ifelse(bin_continuous == FALSE & 
                                                     use_density == TRUE, 
                                                     "kernel density", 
                                                     "normal approximation"))))) %>%
             fct_relevel("2 quantile", "3 quantile", "4 quantile",
                         "5 quantile", "6 quantile", "2 equally spaced",
                         "3 equally spaced", "4 equally spaced",
                         "5 equally spaced", "6 equally spaced",
                         "2 samesource tree", "3 samesource tree",
                         "4 samesource tree", "5 samesource tree",
                         "6 samesource tree")) %>%
    mutate(bin_situation = ifelse(bin_method == "quantile_bins" & 
                                  bin_continuous == TRUE,
                                  "quantile",
                                  ifelse(bin_method == "equally_spaced" & 
                                         bin_continuous == TRUE,
                                         "equally spaced", 
                                         ifelse(bin_method == "tree" & 
                                                bin_continuous == TRUE & 
                                                response == "samesource",
                                                "samesource tree", 
                                                ifelse(bin_method == "tree" & 
                                                       bin_continuous == TRUE & 
                                                       response == "rfscore",
                                                       "rfscore tree", 
                                                       ifelse(bin_continuous == FALSE & 
                                                       use_density == TRUE, 
                                                       "kernel density", 
                                                       "normal approximation")))))) %>%
    mutate(bin_situation = factor(bin_situation)) %>%
    select(situation, bin_situation, bin_continuous:response, case:feature_desc,
           feature_bin:strictly_less, data, prediction)
